---
output: html_document
editor_options: 
  chunk_output_type: console
---
# Results {-}

```{r results, echo=F, message=F, warning=F}
  # Use pandoc for Word documents
  format="pandoc"


knitr::opts_chunk$set(echo = F, message = F, warning = F, cache = F, fig.align = 'center', out.width = '90%', fig.width = 10)

library(bookdown)
library(tidyverse)
library(lubridate)
library(tableone)
library(readxl)
library(yardstick)


number_surveys_posted = 218

questions = c(
  "Age in years",
  "Gender",
  "Ethnic group",
  "How many medicines were you taking?",
  "Prior to the review, how did you feel about your medicines?",
  "How was your medicines review undertaken?",
  "How did you feel when the pharmacist spoke to you about your medicines?",
  "How do you feel about the outcome of the review?",
  "After the review, how do you feel about your medicines now?",
  "Change in how respondent feels about medicines before/after review"
)

df <- readRDS('data/PEPPR.rds')

df1 <- df %>%
  select(-ID, -Notes, -aware_review, -Eleven) %>%
  mutate(
    # Gender
    Three = case_when(
      grepl("English|Irish", Three) ~ paste0("White: ", Three),
      Three == "Indian" ~ "Asian/Asian British: Indian",
      TRUE ~ NA_character_
    ),
    # "How did you feel about your medicines?" BEFORE review
    Five = case_when(
      grepl("Hopeless|Insecure|Frustrated", Five) ~ "negative",
      Five == "OK"                                ~ "neutral",
      grepl("Grateful|Secure|Safe", Five)         ~ "positive",
      TRUE                                        ~ NA_character_
    ),
    Ten = case_when(
      grepl("Hopeless|Insecure|Frustrated", Ten)  ~ "negative",
      Ten == "OK"                                 ~ "neutral",
      grepl("Grateful|Secure|Safe", Ten)          ~ "positive",
      TRUE                                        ~ NA_character_
    ),
    Seven = case_when(
      grepl("Ignored|Disrespected|Frustrated", Seven) ~ "negative",
      Seven == "OK"                                   ~ "neutral",
      grepl("Empowered|Confident|Optimistic", Seven)  ~ "positive",
      TRUE                                            ~ NA_character_
    ),
    Nine = case_when(
      grepl("Ignored|Disrespected|Frustrated", Nine) ~ "negative",
      Nine == "OK"                                   ~ "neutral",
      grepl("Empowered|Confident|Optimistic", Nine)  ~ "positive",
      TRUE                                           ~ NA_character_
    ),
    change_in_feeling = case_when(
      Five == "positive" & grepl("negative|neutral", Ten) ~ "negative",
      Five == "neutral" & Ten == "negative" ~ "negative",
      Five == Ten ~ "no change",
      Five == "negative" & grepl("neutral|positive", Ten) ~ "positive",
      Five == "neutral" & Ten == "positive" ~ "positive",
      TRUE ~ NA_character_
    ),
    change_during_review = case_when(
      Eight == "7" ~ "no",
      is.na(Eight) ~ NA_character_,
      TRUE ~ "yes"
    )
  )

df2 <- df1 %>% select(-change_during_review, -Eight)
colnames(df2) <- questions
vars <- colnames(df2)
# All are factor variables except for age
factorVars <- colnames(df2)[-1]



summary_table <- CreateTableOne(
  vars = colnames(df2),
  data = df2,
  test = F,
  factorVars = factorVars,
  includeNA = T
)

library(yardstick)



# McNemar Need to talk to Dawn about this...

# paired_data <- df1 %>%
#   filter(!is.na(change_in_feeling), change_in_feeling != "no change") %>%
#   select(change_in_feeling) %>%
#   mutate_all(as.factor) %>% 
#   conf_mat(truth = Five, estimate = Ten, dnn = c("Post-review", "Pre-review"))

# paired_data <- df1 %>%
#   filter(Five != "neutral", Ten != "neutral") %>%
#   select(Five, Ten) %>%
#   mutate_all(as.factor) %>% 
#   conf_mat(truth = Five, estimate = Ten, dnn = c("Post-review", "Pre-review"))

#            Pre-review
# Post-review negative positive
#    negative        2        0
#    positive        4        5

#test <- matrix(c(2,0,0,0.0000000001,23,1,4,3,5), nrow=3, byrow = T)

#mcnemar.test(test, correct = T)

# 	McNemar's Chi-squared test with continuity correction
# 
# data:  paired_data$table
# McNemar's chi-squared = 2.25, df = 1, p-value = 0.1336

```

The first surveys were sent out on the 20th September 2019 and the last, on the 24th March 2020, when the study was paused due to the covid pandemic. Surveys included reviews conducted between the 7th August 2019 and 23rd March 2020. In total, 218/265 (82.3%) of patients who had a CMR received a invitation pack. At the time of study closure on the 23rd July 2020, we had received 48/218 (22.0%) surveys (Table \@ref(tab:summarytable)).


```{r summarytable}

kableone(print(summary_table, showAllLevels = T), format = format, caption = "Summary of survey responses")

```

Of the 48 responses, 37/48 provided responses relating to activities that occured during the review. In most cases no changes were made to medicines, but patients were frequently given advice about how to take their medicines (Figure \@ref(fig:cmr-activity)). However, almost 30% did not know how their CMR was undertaken. It transpired that many reviews **PERHAPS INCLUDE ACTUAL NUMBER FROM PREFACES?** were actually notes-based, where the pharmacist reviews the patient's medical and prescibing records. It is not routine practice to contact patients inform them that this has taken place.


```{r cmr-activity, fig.cap="Activities during CMR"}

cmr_qn <- c(
  "Advice about how to take medicines",
  "Explanation of medicines",
  "1+ medicines stopped",
  "1+ medicines had a change in dose",
  "Medicine administration time changed",
  "1+ medicines were changed for another",
  "No changes were made to my medicines"
)

# df %>%
#   select(Six, Eight) %>%
#   na.omit() %>% count()


summary_activity_df <- df %>%
  dplyr::select(Six, Eight) %>%
  na.omit() %>%
  separate_rows(Eight, sep=",") %>%
  count(Eight) %>%
  mutate(
        name = case_when(
      !is.na(as.integer(Eight)) ~ cmr_qn[as.integer(Eight)],
      TRUE ~ "Don't remember"
    )
  ) %>%
  arrange(desc(n))

# 37 results included here

df %>%
  select(Six, Eight) %>%
  na.omit() %>%
  separate_rows(Eight, sep=",") %>%
  count(Six, Eight) %>%
  group_by(Eight) %>%
  mutate(
    total_n = sum(n),
    name = case_when(
      !is.na(as.integer(Eight)) ~ cmr_qn[as.integer(Eight)],
      TRUE ~ "Don't rember"
    )
  ) %>%
  ggplot(aes(x = fct_reorder(name, total_n, .desc = F), y = n, fill = Six)) +
  geom_col(color = "grey50") +
  scale_y_continuous(name = "Number of responses", labels = seq(0, 20, 2),breaks = seq(0,20,2)) +
  scale_x_discrete(name = "Activity during review") +
  coord_flip() +
  theme_minimal() +
  scale_fill_viridis_d(name = "Review type", breaks = c("Telephone", "F2F", "Don't Know"), labels = c("Telephone", "Face-to-face",  "Unknown")) +
  theme(legend.position = "bottom",  text = element_text(size = 20))


```


## Emotions pre- and post-review

Only 8 patients reported a change in emotion between pre- and post-review and in 7/8 (87.5%) of cases this was a positive change in emotion. Most patients expressed a neutral emotion which did not change as a result of the review (Table \@ref(tab:prim-outcome)).

**NEED ADVICE FROM STATISTICIAN ABOUT MCNEMAR TEST**

```{r prim-outcome}

con_matrix <- df1 %>% filter(!is.na(Five) & !is.na(Ten)) %>% 
  select(Five, Ten) %>% 
  mutate_all(as.factor) %>% 
  conf_mat(truth = Five, estimate = Ten, dnn = c("Post-review", "Pre-review")) 

knitr::kable(con_matrix$table, format = format, caption = "Patient reported emotion pre- and post-medicine review")


```


## Secondary outcome

Table \@ref(tab:olr-table) shows the results of the proportional odds model. Ethnicity was removed from the model since only two respondents reported an ethnicity other than 'White: English/Welsh/Scottish/N. Irish/British'. None of the included terms appeared to significantly affect how patient's felt following a CMR.

```{r ord-regression}

#library(MASS)

ord_df <- df1 %>% 
  dplyr::select(change_in_feeling, One, Two, Three, Six, Seven, change_during_review) %>%
  mutate_if(is.character, factor) %>%
  mutate(
    change_in_feeling = ordered(change_in_feeling, levels = c("negative", "no change", "positive"))
  )

fit <- MASS::polr(change_in_feeling ~ One + Two + Three + Six + Seven + change_during_review, data = ord_df, Hess = T)


olr_result <- tidy(fit, exponentiate = T, conf.int = F, p.values = F)

terms <- c("Age", "Male", "White:English", "Face-to-face", "Telephone", "Neutral", "Positive", "Changes during CMR", "negative|no change", "no change|positive")

olr_result$term <- terms


# A tibble: 10 x 5
#   term               estimate std.error statistic conf.low conf.high coef.type  
#   <chr>                 <dbl>     <dbl>     <dbl>    <dbl>     <dbl> <chr>      
# 1 Age                   1.00       0.05     0.058    0.91       1.11 coefficient
# 2 Male                  1.01       1.01     0.009    0.129      7.89 coefficient
# 3 Face-to-face          0.83       1.18    -0.159    0.082     10.1  coefficient
# 4 Telephone             0.629      1.29    -0.36     0.046      9.33 coefficient
# 5 Neutral               0.47       1.67    -0.453    0.013     16.7  coefficient
# 6 Positive              0.136      1.84    -1.08     0.002      5.85 coefficient
# 7 Changes during CMR    1.19       1.09     0.157    0.145     12.3  coefficient
# 8 negative|no change    0         25.8     -0.43    NA         NA    scale      
# 9 no change|positive    1.36       4.64     0.066   NA         NA    scale      

fit2 <- MASS::polr(change_in_feeling ~ One + Two + Six + Seven + change_during_review, data = ord_df, Hess = T)

olr_result2 <- tidy(fit2, exponentiate = T, conf.int = T) %>%
  mutate_if(is.double, round, 2)

terms2 <- c("Age", "Male", "Face-to-face", "Telephone", "Neutral", "Positive", "Changes during CMR", "negative|no change", "no change|positive")

olr_result2$term <- terms2


# A tibble: 9 x 7
#   term                    estimate std.error statistic conf.low conf.high coef.type  
#   <chr>                      <dbl>     <dbl>     <dbl>    <dbl>     <dbl> <chr>      
# 1 One                        1.00       0.05     0.058    0.91       1.11 coefficient
# 2 TwoMale                    1.01       1.01     0.009    0.129      7.89 coefficient
# 3 SixF2F                     0.83       1.18    -0.159    0.082     10.1  coefficient
# 4 SixTelephone               0.629      1.29    -0.36     0.046      9.33 coefficient
# 5 Sevenneutral               0.47       1.67    -0.453    0.013     16.7  coefficient
# 6 Sevenpositive              0.136      1.84    -1.08     0.002      5.85 coefficient
# 7 change_during_reviewyes    1.19       1.09     0.157    0.145     12.3  coefficient
# 8 negative|no change         0         25.8     -0.43    NA         NA    scale      
# 9 no change|positive         1.36       4.64     0.066   NA         NA    scale    

```

```{r olr-table}

knitr::kable(olr_result2 %>% filter(coef.type == "coefficient") %>% mutate(`95% CI` = paste0(conf.low,'--',conf.high)) %>% dplyr::select(term, estimate, `95% CI`),
             format = format, 
             caption = "Proportional odds model")

```




```{r}


# ## Raw results
# 
# Results of summary(fitted model) and then tidy equivalent with coefficients exponentiated.
# 
# + One = Age in years
# + Two = gender
# + Three = ethnicity
# + Six = Method of review
# + Seven = Emotion during review
# + change_in_review = Whether any change (apart from ‘no change to medicines’ was selected)
# 
# summary(fit)
# 
# # Model with ethnicity
# olr_result %>% select(-coef.type)
# 
# 
# # Mode without ethnicity
# 
# summary(fit2)
# 
# olr_result2 %>% select(-coef.type)


```
